Classification and Regression Trees and Beyond

### 2020-07-01 pkg/partykit/inst/ULGcourse-2020/slides_tree.Rnw
use Therneau & Atkinson 1997 reference
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3029 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: f78491190020eb28121edb7da05e7e24dbdb78bd

@@

Therneau T, Atkinson B (2019). 
  \dquote{{rpart}: Recursive Partitioning and Regression Trees.}
  \url{https://CRAN.R-project.org/package=rpart}

>>>>

Therneau T, Atkinson B (1997). 
  \dquote{An Introduction to Recursive Partitioning Using the {rpart} Routine.}
  Technical Report~61, Section of Biostatistics, Mayo Clinic, Rochester.
  \url{http://www.mayo.edu/hsr/techrpt/61.pdf}

@@
